Title goes here

### 2016-10-23 paper/paper.tex
Updated authors
PAPER: stuff

\title{Title goes here}
\author{Filippo Sestini \\ Vrije Universiteit \\ email@host.com \and
  Davide Dal Bianco \\ Vrije Universiteit \\ email@host.com}

@@

\section{Introduction}
% what is this project about and why is it interesting?

@@

Our approach of clustering together routes represented as sequences of sectors
is inspired by the Leader Algorithm described in [reference], but differs from
it in some ways. Sectors in [reference] are bounded airspace regions under the
control of a single air traffic controller or small team, hence they cover a
relatively large area. Flights with such subdivision usually go through 5--10
sectors. Our sectors are smaller --- each flight has approximately 20--40 of
them --- therefore they represent a much more fine-grained subdivision of the
world map.

In [reference], distance between two routes is computed as a simple editing
distance between a lexical representation of routes. With smaller sectors,
however, comes the need to take other factors into account. An extreme example
of why this is needed is given by two routes that are almost parallel and at
distance of slightly more than 10 km. In our subdivision in sectors of 10 km by
10 km, these two routes would end up represented by a sequence with almost no
common sectors, even though they are actually very similar. A simple editing
distance function would assign the same value to this pair of routes, as well as
another pair of routes much more distant and different from each other.

>>>>

\title{Title goes here}
\author{Filippo Sestini \\ Vrije Universiteit Amsterdam \\ f.sestini@student.vu.nl \and
  Davide Dal Bianco \\ Vrije Universiteit Amsterdam \\ d.dalbianco@student.vu.nl}

@@

\section{Introduction}

@@

Our approach of clustering together routes represented as sequences of sectors
is inspired by the Leader Algorithm described in \cite{routeclustering}, but
differs from it in some ways. Sectors in \cite{routeclustering} are bounded
airspace regions under the control of a single air traffic controller or small
team, hence they cover a relatively large area. Flights with such subdivision
usually go through 5--10 sectors. Our sectors are smaller --- each flight has
approximately 20--40 of them --- therefore they represent a much more
fine-grained subdivision of the world map.

In \cite{routeclustering}, distance between two routes is computed as a simple
editing distance between a lexical representation of routes. With smaller
sectors, however, comes the need to take other factors into account. An extreme
example of why this is needed is given by two routes that are almost parallel
and at distance of slightly more than 10 km. In our subdivision in sectors of 10
km by 10 km, these two routes would end up represented by a sequence with almost
no common sectors, even though they are actually very similar. A simple editing
distance function would assign the same value to this pair of routes, as well as
another pair of routes much more distant and different from each other.
